---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# accelPrint

<!-- badges: start -->
[![R-CMD-check](https://github.com/lilykoff/accelPrint/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/lilykoff/accelPrint/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of accelPrint is to do fingerprinting for acceleration and walking.

## Installation

You can install the development version of accelPrint from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("lilykoff/accelPrint")
```

## Example

This is a basic example which shows you how to use the package

### Get walking bouts from raw accelerometry data 

We compute the bouts and plot the signal from the first 10s. There is no data plotted in second 5 because no steps were identified by ADEPT in that second. 

```{r example}
library(accelPrint)
library(ggplot2)
library(dplyr)
# load example data 
data(raw_accel)
# run the get walking function
walking_bouts = accelPrint::get_walking(raw_accel, parallel = TRUE)
head(walking_bouts) 

walking_bouts %>% 
  slice(1:(10 * 100)) %>% # take first 10 s 
  mutate(vm = sqrt(x^2 + y^2 + z^2)) %>% # compute vector magnitude
  ggplot(aes(x = time, y = vm, group=second)) + 
  geom_line() + 
  scale_x_datetime(date_labels = "%S") + 
  labs(x = "Time (s)", y = "Vector magnitude (g)")

```

### Get fingerprint predictors from walking bouts 

Each column is one grid cell/lag combination, each row is a second. Each entry is the number of points in the grid cell for that lag. Column names are formatted as `range_lagrange_lag`, so `[0,0.25]_[0,0.25]_15` corresponds to number of points in range acceleration $\in [0,0.25]$, lag acceleration $\in [0,0.25]$, for a lag of 15 samples. 

```{r}
# run the get grid cells function on the walking bouts
# specify lags of 0.15, 0.30, 0.45 seconds and grid cell size of 0.25g 
fingerprint_predictors = compute_grid_cells(walking_bouts, 
                                            lags = c(0.15, 0.30, 0.45), 
                                            cell_size = 0.25,
                                            max_vm = 3)

head(fingerprint_predictors) 
```


```{r}
# plot 
plot_grid_cells(fingerprint_predictors)
```

